Unified Understanding of the Dielectric Nature of Two-Dimensional Materials

### 2018-10-26 paper.tex
Reorder the theoretical part

It is also worth mentioning that the dielectric properties of 2D
materials are also often modeled using an effective medium approach,
which treats the 2D material as a slab with effective permittivity
$\varepsilon_{\mathrm{2D}}$ and thickness $\delta$
\cite{Sharma_1985,Cudazzo_2011_screening_2D,Matthes_2016,Trolle_2017_eps_subst,Laturia_2018}. Such
methods require \textit{a priori} determination of $\delta$, a
quantity with controversial definitions \cite{Mas_Ballest__2011}. In
such approaches, $\varepsilon_{\mathrm{2D}}$ and $\delta$ have to be
determined by fitting the $L$-dependent data of
$\varepsilon_{\mathrm{SL}}$, which is not only computational
expensive, but also fails to capture the anisotropy of the 2D
dielectric properties (see Supplementary Section S1). On the
other hand, calculating 2D polarizabilities requires no knowledge of
$\delta$ (see Eqs. \ref{eq:alpha-para-def} and
\ref{eq:alpha-perp-def}), and correctly presents the anisotropy of 2D
dielectric nature that $\alpha^{\parallel} > \alpha^{\perp}$.  With
the polarizability as the true descriptor of 2D dielectric properties,
we will reveal the universal Moss-like relation of 2D materials.

\subsection{2D Moss Relations}
\label{sec:first-principles}

We study several types of 2D materials of different electronic and
optical properties as show in Figure \ref{fig-2}, including transition
metal dichalcogenides (TMDCs, with the formula MX\(_{\text{2}}\),
where M is a metal in group 4, 6, 10 and X=O, S, Se, Te), metal
monochalcogenides (Ga$_{2}$S$_{2}$, Ga$_{2}$Se$_{2}$), cadmium halides
(CdX$_2$, X=Cl, I), hexagonal boron nitride (BN), graphene derivatives
(fluorographene (C$_{2}$F$_{2}$), graphane (C$_{2}$H$_{2}$)),
phosphorene (P$_{4}$) and thin layer organic-inorganic perovskites
(ABX$_{3}$).  For the TMDCs, we consider 2 lattice phases, namely the
2H (P\(\bar{6}\)m2 space group) and 1T (P3m1 space group).  The static
2D polarizabilities are calculated from the static dielectric response
of the selected 2D materials using density functional theory (DFT)
with the Heyd-Scuseria-Ernzerhof hybrid functionals (HSE06) using the
Vienna Ab Initio Simulation Package (VASP) including spin-orbit
coupling to avoid limitations on the description of band gaps and
dielectric functions (see Methods for details).

Similar to the treatment of quantum wells (QW), the wavefunction of an
isolated 2D material $\psi(\mathbf{r})$ can be separated into the in-
and out-of-plane components \cite{davies_physics_1997}
$\psi^{\parallel}(\mathbf{\rho})$ and $\psi^{\perp}(z)$, such that
$\psi=\psi^{\parallel}\psi^{\perp}$, where $\mathbf{\rho}=(x, y)$ is
the in-plane coordinate. Using the Bloch theorem, the periodic
$\psi^{\parallel}(\mathbf{\rho})$ can be further expressed as
$\psi^{\parallel}(\mathbf{\rho})=e^{ik\rho}u(\rho)$, where $k$ is the
in-plane wave vector and $u(\rho)$ is periodic function in the
xy-plane. According to the random phase approximation (RPA)

@@

$\mathcal{H} = -\hbar^{2}/2m^{*} \nabla^{2} + V(z)$, where $\hbar$ is
the reduced Planck constant, $m^{*}$ is reduced mass and $V(z)$ is the
confined Coulombic potential along the z-direction created by the

@@

simple particle-in-well model, we show that both the numerator and

@@

(details see Supplementary Section S4). We further prove,
using both quantum mechanical and fundamental electrostatic models,
that $\alpha^{\perp}$ is actually proportional to the size of
potential confinement (details see Supplementary Section
S4), which we may relate with the thickness $\delta$ of
the 2D material. Now we may finally propose the 2D analog of the Moss
relation with both in- and out-of-plane polarizations:

@@

which form the main conclusion of this work.

>>>>

It is also worth mentioning that the dielectric properties of 2D
materials are also often modeled using an effective medium approach,
which treats the 2D material as a slab with effective permittivity
$\varepsilon_{\mathrm{2D}}$ and thickness $\delta$
\cite{Sharma_1985,Cudazzo_2011_screening_2D,Matthes_2016,Trolle_2017_eps_subst,Laturia_2018}. Such
methods require \textit{a priori} determination of $\delta$, a
quantity with controversial definitions \cite{Mas_Ballest__2011}. In
such approaches, $\varepsilon_{\mathrm{2D}}$ and $\delta$ have to be
determined by fitting the $L$-dependent data of
$\varepsilon_{\mathrm{SL}}$, which is not only computational
expensive, but also fails to capture the anisotropy of the 2D
dielectric properties (see Supplementary Section S1). On the other
hand, calculating 2D polarizabilities requires no knowledge of
$\delta$ (see Eqs. \ref{eq:alpha-para-def} and
\ref{eq:alpha-perp-def}), and correctly presents the anisotropy of 2D
dielectric nature that $\alpha^{\parallel} > \alpha^{\perp}$.  With
the polarizability as the true descriptor of 2D dielectric properties,
we will reveal the universal Moss-like relation of 2D materials from
both theoretical and first principles studies.

\subsection{Polarizability-Based Theoretical Model}
In this section we theoretically investigate the existence of the 2D
Moss-like relations, based on the 2D polarizability.  Due to its
highly anisotropic nature, the wavefunction of an isolated 2D material
$\psi(\mathbf{r})$ can be separated into the in- and out-of-plane
components, similar to the treatment of quantum wells
(QW),\cite{davies_physics_1997} such that
$\psi^{\parallel}(\boldsymbol{\rho})$ and $\psi^{\perp}(z)$, such that
$\psi=\psi^{\parallel}\psi^{\perp}$, where $\boldsymbol{\rho}=(x, y)$
is the in-plane coordinate. Using the Bloch theorem, the periodic
$\psi^{\parallel}(\boldsymbol{\rho})$ can be further expressed as
$\psi^{\parallel}(\boldsymbol{\rho})=e^{i\mathbf{k} \cdot
  \boldsymbol{\rho}}u(\boldsymbol{\rho})$, where $\mathbf{k}$ is the
in-plane wave vector and $u(\boldsymbol{\rho})$ is periodic function
in the xy-plane. According to the random phase approximation (RPA)

@@

$\mathcal{H} = -\hbar^{2} \nabla^{2}/2m_{e} + V(z)$, where $\hbar$ is
the reduced Planck constant, $m_{e}$ is electron mass and $V(z)$ is
the confined Coulombic potential along the z-direction created by the

@@

simple particle-in-box model, we show that both the numerator and

@@

(details see Supplementary Section S4). We further prove, using both
quantum mechanical and fundamental electrostatic models, that
$\alpha^{\perp}$ is actually proportional to the size of potential
confinement (details see Supplementary Section S4), which we may
relate with the thickness $\delta$ of the 2D material. Now we may
finally propose the 2D analog of the Moss relation with both in- and
out-of-plane polarizations:

@@

which form the main conclusion of this work. Next, we will validate
the proposed 2D Moss-like relations using first principle
calculations.

\subsection{2D Moss Relations}
\label{sec:first-principles}
We study several types of 2D materials of different electronic and
optical properties as show in Figure \ref{fig-2}, including transition
metal dichalcogenides (TMDCs, with the formula MX\(_{\text{2}}\),
where M is a metal in group 4, 6, 10 and X=O, S, Se, Te), metal
monochalcogenides (Ga$_{2}$S$_{2}$, Ga$_{2}$Se$_{2}$), cadmium halides
(CdX$_2$, X=Cl, I), hexagonal boron nitride (BN), graphene derivatives
(fluorographene (C$_{2}$F$_{2}$), graphane (C$_{2}$H$_{2}$)),
phosphorene (P$_{4}$) and thin layer organic-inorganic perovskites
(ABX$_{3}$).  For the TMDCs, we consider 2 lattice phases, namely the
2H (P\(\bar{6}\)m2 space group) and 1T (P3m1 space group).  The static
2D polarizabilities are calculated from the static dielectric response
of the selected 2D materials using density functional theory (DFT)
with the Heyd-Scuseria-Ernzerhof hybrid functionals (HSE06) using the
Vienna Ab Initio Simulation Package (VASP) including spin-orbit
coupling to avoid limitations on the description of band gaps and
dielectric functions (see Methods for details).
